The Freeplay Sandbox: a Novel Methodology for the Evaluation of Social Robotics

### 2017-10-06 paper.tex
Update on Overleaf.

We introduce in this paper such a task, designed to elicit rich, complex, varied
social interactions while being well suited for interactions with robots and
supporting rigorous scientific methodologies.

@@

The choice of a playful interaction is supported by the wealth of social
situations and social behaviours that \emph{play} elicits. Most of the research
in that field builds on the precursory work of Parten who established five
\emph{stages of play}~\cite{parten1932social}, corresponding to different stages
of development, and accordingly associated to typical age ranges:

\begin{enumerate}
    \item {\bf Solitary (independent) play}, age 2-3: Playing separately from
        others, with no reference to what others are doing.
    \item {\bf Onlooker play}, age 2.5-3.5: Watching others play. May engage in
        conversation but not engaged in doing. True focus on the children at
        play.
    \item {\bf Parallel play} (adjacent play, social co-action), age 2.5-3.5: Playing
        with similar objects, clearly beside others but not with them (near
        but not with others.)
    \item {\bf Associative play}, age 3-4:  Playing with others without
        organization of play activity. Initiating or responding to
        interaction with peers. 
    \item {\bf Cooperative play}, age 4+: Coordinating one's behavior with that
        of a peer. Everyone has a role, with the emergence of a sense of
        belonging to a group. Beginning of "team work."
\end{enumerate}

@@

To mitigate the technical challenges presented by free play interactions in
their most unconstrained version (like high dimensionality and uncertainties),
we have developed a \emph{free-play sandbox}, Figure~\ref{fig|freeplay}: a large
touchscreen (60cm $\times$ 33cm) is used as an interactive surface
(\emph{sandtray} paradigm~\cite{baxter2012touchscreen}). Two participants (either a
pair of children or one child and one robot) play together by freely moving on a
2D plane items (characters and blocks, see Figure~\ref{fig|sandbox}). A
background image depicts a generic empty environment, with different symbolic
zones (water, grass, path, bushes...). Additionally, the children can draw on
the background using a tool applying a color on their touches. The players do
not have any particular task to complete, they are simply invited to freely
play. Importantly, they can play for as long as they wish (for
practical reasons, we have limited the sessions to a maximum of 40 minutes in
our own experiments, see Section~\ref{sec:dataset}).

Capturing all the interactions taking place during the play sessions is possible
and practical with this setup. Even though the children will typically move a
little, the task is fundamentally a face-to-face, spatially delimited,
interaction, and as such simplifies the data collection. For instance, during
our dataset acquisition campaign (120 children, more than 45h of footage), the
children's faces were automatically detected in 97\% [TODO: check that!] of the
recorded frames.

@@

The free-play sandbox follows the sandtray
paradigm~\cite{baxter2012touchscreen}: a large touchscreen (60cm $\times$ 33cm,
with multitouch support) is used as an interactive surface (\emph{sandtray}).
Two children play together by freely moving interactive items
(Fig.~\ref{fig|sandbox}) on the surface. A background image depicts a generic
empty environment, with different symbolic colours (water, grass, beach,
bushes...). By drawing on top of the background picture, the children can change
the environment to their liking. The players do not have any particular task to
complete, they are simply invited to freely play for as long as they want.

\todo{almost identical to 1.3 and mention dataset}

In order to constrain the dataset to a tractable domain, the task is limited to
a dyadic face-to-face interaction.  The resulting interaction space is
nevertheless high-dimensional, with two main foci: the game-related actions
(drawing, manipulating items, telling stories) and the social interactions
(monitoring the other's actions, discussing and agreeing on joint actions,
supportive/antagonistic behaviours, etc.).

@@

focus on abstract socio-cognitive facets (robot
perception and manipulation are simplified); well suited for qualitative and
quantitative analysis using metrics like Słowinski’s Individual Motor Signature
(for behavioural alignment), Anderson's~\cite{anderson2004social} coding of children’s free-play
interactions, with-me-ness (for assessment of co-engagment).

@@

Depending of the focus of the study, two modes of control for the robot are
available. If the interest is on evaluating a specific robot behaviour, the
robot can be autonomously controlled using inputs from the different sensors.
This setup allows to explore the impact of different social behaviours on the
children independently of the 'game policy' controlling by the robot.

On the other hand, if the focus is on the child behaviour and the technical
aspect is of a lower importance, the robot can be controlled by a human rather
than an algorithm. This paradigm, where a human teleoperate a robot to interact
with a naive partner is called Wizard of Oz (WoZ) and is used in numerous
studies to explore the psychologic side of HRI \cite{riek2012wizard}.

@@

\begin{figure*}
    \centering
    \includegraphics[width=\linewidth]{freeplay-sandbox-architecture}
    \caption{Software architecture of the free-play sandbox. Left (purple) nodes
    are tided to the sandtray (game interface (1) and camera drivers (2)). Nodes in the
    centre (green) implement the behaviour of the robot (play policy (3) and robot
    behaviours (4)). Several helper nodes are available, in particular, segmentation of the
    children drawings into zones (5), A* motion planning for the robot to move
    in-game items (6). Nodes are implemented in
    Python (except for the game interface, developed in QML) and inter-process
    communication relies on ROS. 6D poses are managed and exchanged via ROS TF.}

@@

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{rviz-sandtray}
    \caption{The free-play sandbox, viewed at runtime within ROS RViz. The
    current background drawing (bottom left) is published on a regular image
    topic. Simple computer vision is used to segment it into zones (visible in
    the central panel). The poses and bounding boxes of the interactive items
    are published as well, and turned into an occupancy map, used to plan the
    robot's arm motion.
    visualisation tool.}
    \label{fig|rviz}
\end{figure}

\subsection{Interactive game}
The interactive game is coded using QML, and possess main background image on
top of which items (animals, humans and objects) can be moved from one part of
the world to another. The children can also use a drawing mode in which some
create strokes of color on a layer between the background and the items. This
increase the openess of the game as symbolic objects can be added by drawing
(eg. Figure~\ref{fig|sandbox}. The game exposes the image of the background
with the drawing in case of change and the positions of each item as a TF frame.

@@

A detailed description of the dataset is outside of the scope of this paper, and
we only provide hereafter cursory informations on the dataset. Specific details
regarding the methodology and the acquisition procedure can be found on the
dataset website: [hidden for blind review]. The dataset is open and accessible
to any interested researcher.
\todo{Probably add "an anonymised version of the dataser is open..." Reviewers might be concerned about ethics}

@@

This work has been supported by the EU H2020 Marie Sklodowska-Curie Actions
project DoRoThy (grant 657227).

>>>>

In this paper, we introduce such a task, designed to elicit rich, complex, varied
social interactions while being well suited for interactions with robots and
supporting rigorous scientific methodologies.

@@

The choice of a playful interaction is supported by the wealth of social
situations and social behaviours that \emph{play} elicits. Most of the research
in this field builds on the early work of Parten who established five
\emph{stages of play}~\cite{parten1932social}, corresponding to different stages
of development, and accordingly associated with typical age ranges:

\begin{enumerate}
    \item {\bf Solitary (independent) play}, age 2-3: Playing separately from
        others, with no reference to what others are doing.
    \item {\bf Onlooker play}, age 2.5-3.5: Watching others play. May engage in
        conversation but not engage in doing. True focus on the children at
        play.
    \item {\bf Parallel play} (adjacent play, social co-action), age 2.5-3.5: Playing
        with similar objects, clearly beside others but not with them (near
        but not with others.)
    \item {\bf Associative play}, age 3-4:  Playing with others without
        organization of play activity. Initiating or responding to
        interaction with peers. 
    \item {\bf Cooperative play}, age 4+: Coordinating one's behavior with that
        of a peer. Everyone has a role, with the emergence of a sense of
        belonging to a group. Beginning of "team work."
\end{enumerate}

@@

The background image depicts a contextual environment, with different 
zones (for example, water, grass, path, bushes...). Additionally, the children can draw on
the background using a tool of the colour is costumisable. The players do
not have any particular task to complete, they are simply invited to freely
play. Importantly, they can play for as long as they wish (for
practical reasons, we have limited the sessions to a maximum of 40 minutes in
our own experiments, see Section~\ref{sec:dataset}).

Capturing all the interactions taking place during the play sessions is possible
and practical with this setup. Even though the children will typically move a
little, the task is fundamentally a face-to-face, spatially delimited,
interaction, and as such simplifies the data collection. For instance, during
our dataset acquisition campaign (120 children, more than 45h of footage), the
children's faces were automatically detected in 97\% \textcolor{red}{[TODO: check that!]} of the
recorded frames.

@@

% TB: ALSO EXPLAINED ABOVE, THIS PARAGRAPH IS REDUNDANT
%
% The free-play sandbox follows the sandtray
% paradigm~\cite{baxter2012touchscreen}: a large touchscreen (60cm $\times$ 33cm,
% with multitouch support) is used as an interactive surface (\emph{sandtray}).
% Two children play together by freely moving interactive items
% (Fig.~\ref{fig|sandbox}) on the surface. A background image depicts a generic
% empty environment, with different symbolic colours (water, grass, beach,
% bushes...). By drawing on top of the background picture, the children can change
% the environment to their liking. The players do not have any particular task to
% complete, they are simply invited to freely play for as long as they want.

% TB: ALSO EXPLAINED ABOVE, THIS PARAGRAPH IS REDUNDANT
%
% \todo{almost identical to 1.3 and mention dataset}
% In order to constrain the dataset to a tractable domain, the task is limited to
% a dyadic face-to-face interaction.  The resulting interaction space is
% nevertheless high-dimensional, with two main foci: the game-related actions
% (drawing, manipulating items, telling stories) and the social interactions
% (monitoring the other's actions, discussing and agreeing on joint actions,
% supportive/antagonistic behaviours, etc.).

@@

\todo{Very much unfinished section.}
focus on abstract socio-cognitive facets (robot
perception and manipulation are simplified); well suited for qualitative and
quantitative analysis using metrics like Słowinski’s Individual Motor Signature
(for behavioural alignment), Anderson's~\cite{anderson2004social} coding of children’s free-play
interactions, with-me-ness (for assessment of co-engagment).

@@

Depending of the focus of the study, two modes of control for the robot are
available. If the interest is on evaluating a specific robot behaviour, the
robot can be autonomously controlled using inputs from the different sensors.
This setup allows to explore the impact of different social behaviours on the
children independently of the `game policy' controlling by the robot.

On the other hand, if the focus is on the child behaviour and the technical
aspect is of a lower importance, the robot can be controlled by a human rather
than an algorithm. This paradigm, where the robot is tele-operated to interact
with a naive partner is called Wizard of Oz (WoZ) and is used in numerous
studies to explore the psychologic side of HRI \cite{riek2012wizard}.

@@

\begin{figure*}
    \centering
    \includegraphics[width=\linewidth]{freeplay-sandbox-architecture}
    \caption{Software architecture of the free-play sandbox. Left (purple) nodes
    are connected to the sandtray (game interface (1) and camera drivers (2)). Nodes in the
    centre (green) implement the behaviour of the robot (play policy (3) and robot
    behaviours (4)). Several helper nodes are available, in particular, segmentation of the
    children drawings into zones (5), A* motion planning for the robot to move
    in-game items (6). Nodes are implemented in
    Python (except for the game interface, developed in QML) and inter-process
    communication relies on ROS. 6D poses are managed and exchanged via ROS TF.}

@@

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{rviz-sandtray}
    \caption{The free-play sandbox, viewed at runtime within ROS RViz. The
    current background drawing (bottom left) is published on a regular image
    topic. Simple computer vision is used to segment it into zones (visible in
    the central panel). The poses and bounding boxes of the interactive items
    are published as well, and turned into an occupancy map, used to plan the
    robot's arm motion.}
    \label{fig|rviz}
\end{figure}

\subsection{Interactive game}
The interactive game is coded using QML, and displays a main background image on
top of which items (animals, humans and objects) can be moved. 
The children can also use a drawing mode to
create coloured strokes on a layer between the background and the items. This
increases the openess of the game as symbolic objects can be added by drawing
(eg. Figure~\ref{fig|sandbox}. The game exposes the image of the background
with the drawing in case of change and the positions of each item as a TF frame.

@@

A detailed description of the dataset is outside of the scope of this paper, and
we only provide hereafter cursory informations on the dataset. Specific details
regarding the methodology and the acquisition procedure can be found on the
dataset website: \url{https://freeplay-sandbox.github.io/}. The dataset is open and accessible
to any interested researcher.
\todo{Probably add "an anonymised version of the dataser is open..." Reviewers might be concerned about ethics}

@@

Redacted for anonymous review.
%This work has been supported by the EU H2020 Marie Sklodowska-Curie Actions
%project DoRoThy (grant 657227).
